Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-06-03 paper/agujournaltemplate.tex
Remake error figure

\journalname{Geochemistry, Geophysics, Geosystems}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/error_PWS_PWS.eps}
\caption{Map of the residuals from the linear regression fitting all the depths to a plane.}
\label{pngfiguresample}
\end{figure}

>>>>

\journalname{JGR: Solid Earth}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/error_PWS_PWS.eps}
\caption{Map of the residuals from the linear regression fitting all the depths to a plane. Residuals are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}
